Producer App connecting to Apache Kafka broker This application functions as a producer to our Kafka broker, it is a GET request that takes in a message and pushes it to the Kafka topic that the consumer is listening to\+: the URL to the prosucer is\+: \href{http://34.198.166.4/message/{message}}{\texttt{ http\+://34.\+198.\+166.\+4/message/\{message\}}} Where \textquotesingle{}\{message\}\textquotesingle{} is whatever you please. If you receive a 500 error it is likely that our AWS instance that is running the broker is stopped, as it costs a decent amount to keep running 24/7,so we shut it down when not developing or testing.

{\bfseries{Release Notes}} Version 1.\+0.\+0-\/SNAPSHOT\+: In this version our producer is mapped as a GET request that takes in a message String and pushes that string onto our broker\textquotesingle{}s topic.

Milestone 1\+: Milestone was environment setup(Docker/\+Kafka). Milestone 2\+: In this version mapping is baseurl/flighticao/\{flighticao\}. Where the flight icao is the flight you wish to collect data on. The producer will then send the message received from aviation stack api to a new topic to be used by consumer applciation. Milestone 3\+: In milestone 3 we implemented we implemented a function that will search the API for flights with live flight data and will connect to the broker. Milestone 4\+: In milestone 4 we inegrated job scheduling for updating tracked flights. We also inegrated a webscoket that communicates with the front end in order for the producer to keep track of flights the user wants to see. Milestone 4\+: General bug fixes and code clean up. 